NLTK: The Natural Language Toolkit

### 2002-05-06 technical/acl2002/acl02.tex
- Added section on type checking - Added comments on visualization not needing to be simple - Moved chart parsing figure to put it on the same page as the   discussion of it - Minor changes
svn/trunk@552

% To do:
%   - Write up other approaches
% We assume that the user is familiar with the acronym ``NLP;'' is
% that ok?

% Outline:
%   - abstract (summary, above.)
%   - introduction
%   - choice of programming language
%   - design criteria
%   - modules
%   - uses
%     - assignments/projects
%     - class demonstrations
%   - evaluation
%   - other approaches
%   - conclusion

@@

Three modules provide implementations for these abstract interfaces.
The \texttt{srparser} module implements a simple shift-reduce parser.
The \texttt{chartparser} module provides a flexible parser that uses a
\emph{chart} to record hypotheses about syntactic constituents.  And
the \texttt{rechunkparser} module defines a transformational
regular-expression based implementation of the chunk parser interface.

@@

@@

% jb: this is broken up oddly.

Visualization modules define graphical interfaces for viewing and
manipulating data structures, and graphical tools for experimenting
with NLP tasks.  The \texttt{draw.tree} module provides a simple
graphical interface for displaying tree structures; and the
\texttt{draw.tree\_edit} module provides an interface for building and
modifying tree structures.  The \texttt{draw.plot\_graph} module can be
used to graph mathematical functions.  The \texttt{draw.fsa} module
provides a graphical tool for displaying and simulating finite state
automata.  The \texttt{draw.chart} module provides an interactive
graphical tool for experimenting with chart parsers.

@@

\subsection{Assignments and Projects}

@@

\subsection{Advanced projects}

@@

@@

%Problems: available corpus data, ...
%
%Other strengths / weaknesses

@@

%Future work: 
We plan to continue extending the breadth of materials covered by the
toolkit.  We are currently working on NLTK modules for Hidden Markov
Models, probabilistic parsing, and tree adjoining grammars.  We also
plan to increase the number of algorithms implemented by some existing
modules, such as the text classification module.

Finding suitable corpora is a prerequisite for many student
assignments and projects.  We are therefore putting together a
standard collection of large, clean, open-source corpora, containing
corpora appropriate for every module defined by the toolkit.

>>>>

% To do:
%   - Write up other approaches
%   - Write up advanced projects section

% Outline:
%   - abstract (summary, above.)
%   - introduction
%   - choice of programming language
%   - design criteria
%   - modules
%   - uses
%     - assignments
%     - class demonstrations
%     - projects
%   - evaluation
%   - other approaches
%   - conclusion

@@

Three modules provide implementations for these abstract interfaces.
The \texttt{srparser} module implements a simple shift-reduce parser.
The \texttt{chartparser} module provides a flexible parser that uses a
\emph{chart} to record hypotheses about syntactic constituents.  And
the \texttt{rechunkparser} module defines a transformational
regular-expression based implementation of the chunk parser interface.
% [EL] Add the PCFG parser(s) to this once I'm done with my 630 project

@@

\subsection*{Type Checking}

% [EL] This could use another pass or two. :)
Debugging time is an important factor in the toolkit's ease of use.
To reduce the amount of time students must spend debugging their code,
we provide a type checking module, which can be used to ensure that
functions are given valid arguments.  The type checking module is
used by all of the basic data types and processing classes.

Since type checking is done explicitly, it can slow the toolkit down.
However, when efficiency is an issue, type checking can be easily
turned off; and with type checking is disabled, there is no
performance penalty.

@@

Visualization modules define graphical interfaces for viewing and
manipulating data structures, and graphical tools for experimenting
with NLP tasks.  The \texttt{draw.tree} module provides a simple
graphical interface for displaying tree structures.  The
\texttt{draw.tree\_edit} module provides an interface for building and
modifying tree structures.  The \texttt{draw.plot\_graph} module can be
used to graph mathematical functions.  The \texttt{draw.fsa} module
provides a graphical tool for displaying and simulating finite state
automata.  The \texttt{draw.chart} module provides an interactive
graphical tool for experimenting with chart parsers.

% [EL] This still needs work...
The visualization modules provide interfaces for interaction and
experimentation; they do not directly implement any NLP data
structures or tasks.  Simplicity of implementation is therefore less
of an issue for the visualization modules than it is for the rest of
the toolkit.

@@

\subsection{Assignments}

@@

\subsection{Advanced Projects}

@@

% [EL] FILL THIS IN!!!!

@@

@@

% [EL] Add something saying explicitly that there's still a lot to
% do?  (In response to reviewer comment)
%Future work: 
We plan to continue extending the breadth of materials covered by the
toolkit.  We are currently working on NLTK modules for Hidden Markov
Models, probabilistic parsing, and tree adjoining grammars.  We also
plan to increase the number of algorithms implemented by some existing
modules, such as the text classification module.

Finding suitable corpora is a prerequisite for many student
assignments and projects.  We are therefore putting together a
standard collection of large, clean, open-source corpora, containing
data appropriate for every module defined by the toolkit.
